---
title: "CLT"
author: "Diego Martinez"
date: '06/23/22'
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(lattice)
data("imagpop")
```

```{r}
KK_data <- imagpop$kkardashtemp
my1000 <- sample(KK_data, size = 1000, replace=T)
densityplot(my1000,main="original data")

```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

No it's not unimodal. It's bimodal. There are two peaks. Both peaks are the same size. There are 0 outliers in the plot. 


Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages. 

```{r}
numb = 2
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

No the plot isn't unimodal. The plot is trimodal. There are 3 peaks. The 3 peaks are not all the same. The peak in the middle is the largest peak and stands out the most. The two at the side are equal size to each other. 
 

Do this again for 4 random samples

```{r}
numb = 4
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
```

There are 3 main peaks. There are 2 semi-forming peaks at the side. This plot is trimodal because there are 3 distinctive peaks. The main peak (in the middle) is larger than the rest. It reaches about .025.  The two at the side are the same size and reach at about .0175. 

Then again for 9 random samples

```{r}
numb = 9
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
```

This is unimodal. Since there is 1 distinctive peak. It reaches about .029. There are 3 minor peaks. All 4 peaks have different values, none of them are the same size. 

then 16 random samples

```{r}
numb = 16
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
```
Yes this graph is unimodal. There is only 1 peak so there can't be a comparison in size. 


finally for 36 random samples.

Write a summary paragraph describing what you observed and how it relates to the central limit theorem.

Be sure to comment on both the mean and standard deviation of the sample averages - the CLT makes a statement about what to expect from both.

 

Then submit the link to your github project  to canvas to complete this assignment.